### 2017-04-17 paper1.tex
Add files via upload

Within urban climatology, a combination of satellite, aerial, and ground-based thermal remote sensors have been integral in elucidating the spatial \cite{Roth1989}, temporal \cite{Peng2012}, and geometric \cite{Voogt1997} effects of the built environment on land T\textsubscript{surf}; in evaluating and partitioning urban surface energy balances \cite{BastiaanssenW.G.M.1998, Yamaguchi2005} and; in characterizations of the relationship between surface and \gls{blayer} air temperatures (T\textsubscript{air}) \cite{Stoll1992}. These advances have been aided by substantial improvements in sensor spatial, spectral, and radiometric resolutions, and by the proliferation of both large-scale public satellite remote sensing campaigns and low-cost aerial and near-ground thermography. However, in spite of it's widespread usage, several questions concerning the use and validity of urban remote thermal remote sensing, first posed in Roth et al. 1989 \citet{Roth1989}, have yet to be sufficiently answered, viz,

@@

Although most thermal remote sensors operate within one of the \gls{atmwind}[s] - where atmospheric effects are minimal - virtually any remote sensed TIR signal is subject to radiative effects from the layer of atmosphere between the surface and the sensor. Over much of the thermal infrared \gls{waveband} the atmosphere emits radiation and absorbs a fraction of radiation emitted by the surface. Thus, a remote sensed TIR signal almost certainly not equal to the ground emitted signal. Spectral radiance received by a sensor at height ($z$) can be described by a function deviating from a Planck curve defined by T\textsubscript{surf} based on the spectral transmittance of the intervening atmosphere, with the magnitude of that deviation determined by the difference between Planck curves calculated from T\textsubscript{surf} and ambient T\textsubscript{air}. A radiative transfer code, such as MODTRAN \cite{Berk1987}, can be used to model the effect of the atmosphere on a remote sensed TIR signal. Radiative transfer simulations run in MODTRAN version 4.1 for two path lengths are shown in figure \ref{spectairtsurf}, for spectral radiance emitted from a planar surface at 300 \si{kelvin} through an isothermal atmosphere at 290 \si{\kelvin}, water vapor content of 12 \si{\gram\per\meter\cubed}, and aerosol and trace gas profiles from the mid-latitude summer standard atmosphere \cite{Kantor1962}. At both short and long path lengths, radiance in each band shows some deviation from the ground emitted signal. Larger deviations are observed at longer path lengths, where a significant portion of the resulting signal is emitted from that atmosphere, even in bands with high spectral transmittance. Long path lengths and a less transmissive atmosphere increase the potential for deviation in a remote sensed TIR signal from the ground emitted signal, while the difference between T\textsubscript{air} and T\textsubscript{surf} determines the resulting magnitude of atmospheric influence.

\begin{figure}[H]
	\includegraphics[width=\textwidth]{spectairtsurf}
	\caption{At-sensor spectral directional radiances computed in MODTRAN 4.1 \cite{Berk1987} for short (30 \si{m}) and long (3000 \si{m}) path lengths (z) with Planck curves indicating spectral radiances at T\textsubscript{surf} = 300 \si{K} and T\textsubscript{air} = 290 \si{K}.}
	\label{spectairtsurf}
\end{figure}

Atmospheric effects can lead to differences between the 'true' radiometric T\textsubscript{surf} and the remote sensed T\textsubscript{surf} of over 10 \si{K} for satellite platforms \cite{Cooper1989} and over 6 \si{K} for near-ground sensors \cite{Meier2011}. Moreover, because atmospheric effects are a function of non-uniform and spatiotemporally variant surface and atmospheric properties, their associated errors change depending on instrument type, surface-sensor geometry, study location, and ambient conditions. As intersite and time-continuous analysis is a significant goal of most thermal remote sensed studies (urban or otherwise) these effects cannot be ignored.

Spectral transmission of longwave radiation through a given layer of atmosphere is dependent on total column absorber content (the principal broadband TIR absorbers are H\textsubscript{2}O, CO\textsubscript{2}, and to a lesser extent O\textsubscript{3}, N\textsubscript{2}O, CO, CH\textsubscript{4}, and O\textsubscript{2} \cite{Miskolczi1993}). Holding vertical absorber content constant through a layer of atmosphere, variation in band-by-band TIR transmittance with path length is greatest at urban scales (approximately 1 to 50 \si{\meter}), where transparent spectral bands can quickly become opaque with small changes in path length or absorber content - illustrated in figure \ref{spectransheight}. Thus, transmittance of TIR near the surface is highly dependent on surface-sensor geometry, instrument spectral response, and atmospheric absorber content. Indeed, accurate assessment of atmospheric influence on TIR may be most complex when measured near the surface.

@@

Radiation passing through a layer of atmosphere from an emitting surface towards a sensor can be described in a number of ways: \textit{Spectral directional radiance} $R^\uparrow_z (\lambda, \theta, \phi)$, at height $ z $, wavelength $\lambda$ and from a direction defined by viewingzenith angle \(\theta\), and azimuth angle \(\phi\) is commonly written as

@@

TIR received by a remote sensor can be related to a surface temperature in a number of ways --- each producing different conceptions of T\textsubscript{surf} from different instrument and sensor types. As such, the term "surface temperature" with respect to a remote sensed TIR is vague and can refer to several definitions of "surface" and "temperature". Thus, proper terminology must be attached to land T\textsubscript{surf} inferred from TIR. Definitions and nomenclature conventions for multiple methods for T\textsubscript{surf} retrieval are discussed at length in Norman \& Becker, (1995) \cite{Norman1995}.

@@

A large number of correction routines have been developed to remove atmospheric and emissivity effects from aerial and satellite TIR signals and derive accurate T\textsubscript{rad}. Methods range from simple mono- \cite{Qin2001} and split-window \cite{Wan1996} routines for single- and multi-channel remote sensors, to schemes that integrate a radiative transfer code to isolate the surface emitted signal from interfering signals. Boundary conditions are standard across most correction methods: generally requiring vertical profiles of T\textsubscript{air}, humidity, pressure, and aerosol content to remove atmospheric effects, and surface radiative properties to correct for emissivity effects. However, correction methods are often instrument (or, at the very least, least platform) specific and difficult to generalize across sensor and platform types. Few methods exist for correction of ground based remote sensed TIR --- none of which are robust enough to correct irradiances measured from a near-ground wide-\gls{fov} (FOV) radiometer mounted to view rough terrain.

@@

Several multi-LOS correction routines have been developed for to remove atmospheric effects on near-ground remote sensed TIR: Meier et al., 2011 describes a correction method for oblique angled thermal imagery of urban terrain \cite{Meier2011}. In the method, spatially distributed LOS geometries were calculated by linking each image pixel to the corresponding 3-d coordinates of its viewpoint on a digital building model (DBM). Path lengths were then calculated as the distance between each pixel's corresponding location on the DBM and the sensor represented as the vanishing point of a 3-dimensional pyramidic projection from the sensor's location in the DBM. A pixel-by-pixel correction was then applied to remove atmospheric effects and retrieve T\textsubscript{rad} for each pixel at 30 minute intervals, resulting in a time-continuous climatology of urban T\textsubscript{rad}. However, the method uses thermal images in conjunction with a DBM to calculate path length geometries for each pixel's LOS - a technique not possible with a pyrgeometer, which returns a single integrated value over the sensor FOV. Moreover, the target instrument operates over a narrow waveband with relatively uniform spectral sensor response, reducing the magnitude and variance in atmospheric transmission over the sensor response curve. Thus, the method is not directly generalizable to correct TIR measured via pyrgeometer.

Kotani \& Sugita, 2009 describes a method for correction of wide-FOV (pyrgeometer) TIR irradiances \cite{Kotani2009a} over a homogeneous planar surface. In this method, path lengths were calculated for six sensor heights. Radiances were then modeled using LOWTRAN initialized at $5^{\circ}$ intervals and integrated over the hemisphere to retrieve irradiances for a suite of T\textsubscript{surf}, and ambient T\textsubscript{air} and humidities. The resulting lookup table (LUT) of values is then used to correct $L_z$ and quantify atmospheric effects on remote sensed $L_z$ measured from several sensor heights. Methods outlined in Meier et al., 2011 and Kotani \& Sugita, 2009 are limited to narrow-FOV thermal imagers and planar terrain respectively. A method which combines Meier et al., 2011's representation of complex surface geometry and Kotani \& Sugita, 2009's broadband hemispherical integration is needed for atmospheric correction of urban TIR measured via downward facing pyrgeometer.

@@

To calculate surface-sensor geometries, the Surface-Sensor-Sun Urban Model (SUM) \cite{Soux2004} is initialized with a simplified, orthogonal 3-dimensional DBM representing surface geometry of the area surrounding the sensor. SUM uses a four-dimensional array to represent surface morphology with three spatial dimensions ($x$, $y$, and $z$), with $z$ representing height above the $x$, $y$ plane. An additional fourth dimension is used to store information describing each cell (in this case, distance from the point to the sensor). After specifying sensor position and FOV, the model determines which patches have an unobstructed line of sight to the sensor and calculates distance from "seen" patches to the sensor. Path lengths are binned at 5$^{\circ}$ increments of zenith angle and averaged to return an azimuthally-independent mean path length for each bin. In addition, while simulating path length geometries, SUM calculates view factors for each solid angle "slice", which are later used to weight 2-dimensional angular radiances in the hemispherical integration post-processing steps.

@@

\subsection{Modeling hemispherical irradiances}
With path length geometries calculated in SUM, irradiances are modeled for each time step using version 4.1 of the MODerate resolution atmospheric TRANsmission radiative transfer code (MODTRAN) \cite{Berk1987}. At each time-step, a range of potential temperatures is specified (T\textsubscript{spec}) based on T\textsubscript{hem, b} calculated from the measured irradiance with

@@

After the LUT is defined, at-sensor spectral radiances for each path length/zenith angle are modeled at an emissivity of 0.95 over a waveband of 0 - 2300 \si{cm^{-1}} for each T\textsubscript{spec}. Profiles of T\textsubscript{air} and humidity are retrieved from 30-minute averages of conditions observed at the Sperrstrasse site. Aerosol, trace gas absorber, and above-sensor T\textsubscript{air} and humidity conditions are defined by the mid-latitude summer standard atmosphere when daytime T\textsubscript{air, max} \textgreater 10 \si{\degreeCelsius} (the mid-latitude winter profile is substituted on days where T\textsubscript{air, max} \textless 10 \si{\degreeCelsius}) \cite{Kantor1962}.

@@

MODTRAN has been shown to effectively model near-ground radiative transfer at urban-scale path lengths in 2-dimensions \cite{Hoch2005} \cite{Hoch2007}. However, the method described in this paper accounts for complex 3-dimensional surface geometry, which can exert significant influence on atmospheric transmittance. In addition, the method includes significant post-processing to weight and integrate point-to-point spectral directional radiances to derive 3-dimensional, hemispherical irradiances. Thus, prior to deriving a climatology of urban T\textsubscript{hem, r}, the method was evaluated using profiles of upwelling longwave irradiances measured over a simple planar surface.

@@

For a continuous 14-day period, profiles of up/downwelling short/longwave radiation, T\textsubscript{air}, and humidity measured from 2 \si{m}, 10 \si{m}, and 30 \si{m} were obtained from an instrumented tower in Payerne, Switzerland. The tower, installed over a cultivated field as a part of the Baseline Surface Radiation Network (BSRN), is located approximately 100 \si{\kilo\meter} southwest of the BUBBLE Sperrstrasse tower and is subject to similar summertime conditions as the study site. The study period was chosen to include a comprehensive range of T\textsubscript{surf}, T\textsubscript{air}, humidities, and cloud coverages to represent typical summertime conditions over which atmospheric corrections show the greatest variation. To evaluate the method, we used a modified version of the workflow described in Figure \ref{flow}. First, azimuthally averaged path lengths over a planar surface were calculated in SUM at 5\si{\degree} increments of zenith angle over the sensor FOV for the 10 \si{\meter} and 30 \si{\meter} sensors. For each time step, T\textsubscript{hem, b}, calculated from the lowest $L_z$ measurement, was used to model irradiances at 10 \si{m} and 30 \si{m} at 30-minute intervals using concurrent profiles of T\textsubscript{air} and humidity. Daytime T\textsubscript{air} observed at the highest measurement level was anomalously high compared to typical summertime lapse rates above planar vegetated terrain \cite{Oke1987}. Thus, the T\textsubscript{air} profile was modified to be more representative of the neutral or weakly unstable daytime conditions and weakly stable nighttime conditions. It is likely that these modifications better represent the T\textsubscript{air} profile in the layer between 10 and 30 \si{\meter} than a simple interpolation between the 10 \si{\meter} T\textsubscript{air} and 30 \si{\meter} T\textsubscript{air} measurements. Contrary to the findings in Kotani \& Sugita (2009), an isothermal atmospheric profile was not sufficient to accurately model upwelling fluxes over planar terrain. Although thermal stratification is relatively small by day in an urban canyon \cite{Nakamura1988} - where strong microscale contrasts in T\textsubscript{surf} foster strong canyon mixing and neutral stability - the large daytime T\textsubscript{surf} - T\textsubscript{air} differential and the path-length/transmittance gradient can create large differences in upwelling longwave forced by inter-canyon thermal contrasts - a phenomenon termed radiative divergence. By underestimating near-surface air temperatures and overestimating roughness-layer T\textsubscript{air}, positive divergences by day are underestimated by an isothermal profile. As such, we suggest using a full canyon T\textsubscript{air} and humidity profile to most accurately model near ground fluxes.

@@

\begin{table}[H]
	\centering
	\caption{Statistical performance of the Payerne evaluation. RMSE\textit{\textsubscript{s}} and RMSE\textit{\textsubscript{u}} represent the systemic and unsystematic RMSE respectively. n = 378}
	\label{evalstats}
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}} cccr}
		\toprule 
		Statistic & 10 \si{\meter} flux & 30 \si{\meter} flux & Divergence & Citation \\  \midrule
		Slope & 1.002 & 1.011 & 0.792 &  \\ 
		Intercept, (\si{\watt\per\meter\squared}) & 0.422 & $-$3.560 & $-$0.583 &   \\ 
		\textit{R\textsuperscript{2}} & 0.995 & 0.996 & 0.863 & \\ 
		MAE,  (\si{\watt\per\meter\squared}) & 1.781 & 1.325 & 1.191 & \cite{Willmott1985a} \\ 
		RMSE,  (\si{\watt\per\meter\squared}) & 2.204 & 1.690 & 1.423 & \cite{Willmott1985a} \\ 
		RMSE\textit{\textsubscript{s}},  (\si{\watt\per\meter\squared}) & 1.444 & 0.851 & 1.028 & \cite{Willmott1985a} \\ 
		RMSE\textit{\textsubscript{u}},  (\si{\watt\per\meter\squared}) & 1.666 & 1.460 & 0.985 & \cite{Willmott1985a} \\ 
		\textit{d} & 0.999 & 0.999 & 0.959 & \cite{Willmott2012} \\
		\bottomrule
	\end{tabular*} 
\end{table}

@@

Over both summer and winter seasons, correction magnitudes are strongly correlated with $\Delta$T\textsubscript{hem, r - air}. Figure \ref{season_fit} shows the effect of seasonality and cloud cover on the relationship between correction magnitudes and $\Delta$T\textsubscript{hem, r - air}. The relationship is strongest and most clear in summer when variations in cloud cover can lead to large day-to-day contrasts in solar input and $\Delta$T\textsubscript{surf - air}, which translates into a wide range of correction magnitudes.

Figure \ref{nofit} illustrates the the relationship between correction magnitude and meteorological variables commonly measured as a part of climatological assessments of urban environments. A strong positive relationship is observed between correction magnitudes and incoming solar radiation. T\textsubscript{hem, r} and T\textsubscript{air} display more complex relationships with correction magnitude, with a large cluster of observed correction magnitudes situated at a local minimum between $10$ and $20$ \si{\degreeCelsius}, weakly negative correlation at temperatures lower than $10$ \si{\degreeCelsius}, and weakly positive correlation at temperatures greater than $20$ \si{\degreeCelsius}. Atmospheric water vapor content did not appear to exert significant control over correction magnitudes.

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,
	height=7in,
	keepaspectratio]{bxsac_season_clima_pres}
	\caption{Atmospheric correction magnitudes calculated as the difference between T\textsubscript{hem, r} and T\textsubscript{bright} for the duration of the study period. Grey shading indicates nighttime.}
	\label{bx_ac}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,
	height=7in,
	keepaspectratio]{nofit}
	\caption{Correction magnitude versus meteorological variables for the daytime hours of the study period. }
	\label{nofit}
\end{figure}

@@

%\begin{figure}[H]
%	\centering
%	\includegraphics[width=15cm,
%	height=7in,
%	keepaspectratio]{tc_quarts2}
%	\caption{A comparison of T\textsubscript{surf} from sensor geometries described in Table \ref{weightings}. T\textsubscript{surf} is normalized against complete %T\textsubscript{surf}.}
%	\label{tc_quarts}
%\end{figure}

@@

Mean normalized T\textsubscript{hem, r}, T\textsubscript{plan}, and $\Delta$T\textsubscript{plan - hem, r} are shown in figure \ref{tc_mean_314} along with clear sky and overcast sky case days. While mean T\textsubscript{hem, r} and T\textsubscript{plan} display similar overestimations of T\textsubscript{comp}, under clear sky conditions, overestimation by T\textsubscript{plan} is much larger than that by T\textsubscript{hem, r}.

@@

%As shown in figure \ref{tc_mean},

%\begin{figure}[H]
%	\centering
%	\includegraphics[width=15cm,
%	height=7in,
%	keepaspectratio]{tc_mean3}
%	\caption{Normalized T\textsubscript{hem, r}, T\textsubscript{plan}, and T\textsubscript{plan} minus T\textsubscript{hem, r} averaged over the IOP and for clear sky and overcast case days.}
%	\label{tc_mean}
%\end{figure}

>>>>

Within urban climatology, a combination of satellite, aerial, and ground-based thermal remote sensors have been integral in elucidating the spatial \citep{Roth1989}, temporal \citep{Peng2012}, and geometric \citep{Voogt1997} effects of the built environment on land T\textsubscript{surf}; in evaluating and partitioning urban surface energy balances \citep{BastiaanssenW.G.M.1998, Yamaguchi2005} and; in characterizations of the relationship between surface and \gls{blayer} air temperatures (T\textsubscript{air}) \citep{Stoll1992}. These advances have been aided by substantial improvements in sensor spatial, spectral, and radiometric resolutions, and by the proliferation of both large-scale public satellite remote sensing campaigns and low-cost aerial and near-ground thermography. However, in spite of it's widespread usage, several questions concerning the use and validity of urban remote thermal remote sensing, first posed in \citet{Roth1989}, have yet to be sufficiently answered, viz,

@@

Although most thermal remote sensors operate within one of the \gls{atmwind}[s] - where atmospheric effects are minimal - virtually any remote sensed TIR signal is subject to radiative effects from the layer of atmosphere between the surface and the sensor. Over much of the thermal infrared \gls{waveband} the atmosphere emits radiation and absorbs a fraction of radiation emitted by the surface. Thus, a remote sensed TIR signal almost certainly not equal to the ground emitted signal. Spectral radiance received by a sensor at height ($z$) can be described by a function deviating from a Planck curve defined by T\textsubscript{surf} based on the spectral transmittance of the intervening atmosphere, with the magnitude of that deviation determined by the difference between Planck curves calculated from T\textsubscript{surf} and ambient T\textsubscript{air}. A radiative transfer code, such as MODTRAN \citep{Berk1987}, can be used to model the effect of the atmosphere on a remote sensed TIR signal. Radiative transfer simulations run in MODTRAN version 4.1 for two path lengths are shown in figure \ref{spectairtsurf}, for spectral radiance emitted from a planar surface at 300 \si{kelvin} through an isothermal atmosphere at 290 \si{\kelvin}, water vapor content of 12 \si{\gram\per\meter\cubed}, and aerosol and trace gas profiles from the mid-latitude summer standard atmosphere \citep{Kantor1962}. At both short and long path lengths, radiance in each band shows some deviation from the ground emitted signal. Larger deviations are observed at longer path lengths, where a significant portion of the resulting signal is emitted from that atmosphere, even in bands with high spectral transmittance. Long path lengths and a less transmissive atmosphere increase the potential for deviation in a remote sensed TIR signal from the ground emitted signal, while the difference between T\textsubscript{air} and T\textsubscript{surf} determines the resulting magnitude of atmospheric influence.

\begin{figure}[H]
	\includegraphics[width=\textwidth]{spectairtsurf}
	\caption{At-sensor spectral directional radiances computed in MODTRAN 4.1 \citep{Berk1987} for short (30 \si{m}) and long (3000 \si{m}) path lengths (z) with Planck curves indicating spectral radiances at T\textsubscript{surf} = 300 \si{K} and T\textsubscript{air} = 290 \si{K}.}
	\label{spectairtsurf}
\end{figure}

Atmospheric effects can lead to differences between the 'true' radiometric T\textsubscript{surf} and the remote sensed T\textsubscript{surf} of over 10 \si{K} for satellite platforms \citep{Cooper1989} and over 6 \si{K} for near-ground sensors \citep{Meier2011}. Moreover, because atmospheric effects are a function of non-uniform and spatiotemporally variant surface and atmospheric properties, their associated errors change depending on instrument type, surface-sensor geometry, study location, and ambient conditions. As intersite and time-continuous analysis is a significant goal of most thermal remote sensed studies (urban or otherwise) these effects cannot be ignored.

Spectral transmission of longwave radiation through a given layer of atmosphere is dependent on total column absorber content (the principal broadband TIR absorbers are H\textsubscript{2}O, CO\textsubscript{2}, and to a lesser extent O\textsubscript{3}, N\textsubscript{2}O, CO, CH\textsubscript{4}, and O\textsubscript{2} \citep{Miskolczi1993}). Holding vertical absorber content constant through a layer of atmosphere, variation in band-by-band TIR transmittance with path length is greatest at urban scales (approximately 1 to 50 \si{\meter}), where transparent spectral bands can quickly become opaque with small changes in path length or absorber content - illustrated in figure \ref{spectransheight}. Thus, transmittance of TIR near the surface is highly dependent on surface-sensor geometry, instrument spectral response, and atmospheric absorber content. Indeed, accurate assessment of atmospheric influence on TIR may be most complex when measured near the surface.

@@

Radiation passing through a layer of atmosphere from an emitting surface towards a sensor can be described in a number of ways: \textit{Spectral directional radiance} $R^\uparrow_z (\lambda, \theta, \phi)$, at height $ z $, wavelength $\lambda$ and from a direction defined by viewing zenith angle \(\theta\), and azimuth angle \(\phi\) is commonly written as

@@

TIR received by a remote sensor can be related to a surface temperature in a number of ways --- each producing different conceptions of T\textsubscript{surf} from different instrument and sensor types. As such, the term "surface temperature" with respect to a remote sensed TIR is vague and can refer to several definitions of "surface" and "temperature". Thus, proper terminology must be attached to land T\textsubscript{surf} inferred from TIR. Definitions and nomenclature conventions for multiple methods for T\textsubscript{surf} retrieval are discussed at length in \citet{Norman1995}.

@@

A large number of correction routines have been developed to remove atmospheric and emissivity effects from aerial and satellite TIR signals and derive accurate T\textsubscript{rad}. Methods range from simple mono-window \citep{Qin2001} and split-window \citep{Wan1996} routines for single-channel and multi-channel remote sensors, to schemes that integrate a radiative transfer code to isolate the surface emitted signal from interfering signals. Boundary conditions are standard across most correction methods: generally requiring vertical profiles of T\textsubscript{air}, humidity, pressure, and aerosol content to remove atmospheric effects, and surface radiative properties to correct for emissivity effects. However, correction methods are often instrument (or, at the very least, least platform) specific and difficult to generalize across sensor and platform types. Few methods exist for correction of ground based remote sensed TIR --- none of which are robust enough to correct irradiances measured from a near-ground wide-\gls{fov} (FOV) radiometer mounted to view rough terrain.

@@

Several multi-LOS correction routines have been developed for to remove atmospheric effects on near-ground remote sensed TIR: \citet{Meier2011} describes a correction method for oblique angled thermal imagery of urban terrain. In the method, spatially distributed LOS geometries were calculated by linking each image pixel to the corresponding 3-d coordinates of its viewpoint on a digital building model (DBM). Path lengths were then calculated as the distance between each pixel's corresponding location on the DBM and the sensor represented as the vanishing point of a 3-dimensional pyramidic projection from the sensor's location in the DBM. A pixel-by-pixel correction was then applied to remove atmospheric effects and retrieve T\textsubscript{rad} for each pixel at 30 minute intervals, resulting in a time-continuous climatology of urban T\textsubscript{rad}. However, the method uses thermal images in conjunction with a DBM to calculate path length geometries for each pixel's LOS - a technique not possible with a pyrgeometer, which returns a single integrated value over the sensor FOV. Moreover, the target instrument operates over a narrow waveband with relatively uniform spectral sensor response, reducing the magnitude and variance in atmospheric transmission over the sensor response curve. Thus, the method is not directly generalizable to correct TIR measured via pyrgeometer.

\citet{Kotani2009a} describes a method for correction of wide-FOV (pyrgeometer) TIR irradiances over a homogeneous planar surface. In this method, path lengths were calculated for six sensor heights. Radiances were then modeled using LOWTRAN initialized at $5^{\circ}$ intervals and integrated over the hemisphere to retrieve irradiances for a suite of T\textsubscript{surf}, and ambient T\textsubscript{air} and humidities. The resulting lookup table (LUT) of values is then used to correct $L_z$ and quantify atmospheric effects on remote sensed $L_z$ measured from several sensor heights. Methods outlined in Meier et al., 2011 and Kotani \& Sugita, 2009 are limited to narrow-FOV thermal imagers and planar terrain respectively. A method which combines Meier et al., 2011's representation of complex surface geometry and Kotani \& Sugita, 2009's broadband hemispherical integration is needed for atmospheric correction of urban TIR measured via downward facing pyrgeometer.

@@

To calculate surface-sensor geometries, the Surface-Sensor-Sun Urban Model (SUM) \citep{Soux2004} is initialized with a simplified, orthogonal 3-dimensional DBM representing surface geometry of the area surrounding the sensor. SUM uses a four-dimensional array to represent surface morphology with three spatial dimensions ($x$, $y$, and $z$), with $z$ representing height above the $x$, $y$ plane. An additional fourth dimension is used to store information describing each cell (in this case, distance from the point to the sensor). After specifying sensor position and FOV, the model determines which patches have an unobstructed line of sight to the sensor and calculates distance from "seen" patches to the sensor. Path lengths are binned at 5$^{\circ}$ increments of zenith angle and averaged to return an azimuthally-independent mean path length for each bin. In addition, while simulating path length geometries, SUM calculates view factors for each solid angle "slice", which are later used to weight 2-dimensional angular radiances in the hemispherical integration post-processing steps.

@@

\subsection{Modeling hemispherical irradiances}
With path length geometries calculated in SUM, irradiances are modeled for each time step using version 4.1 of the MODerate resolution atmospheric TRANsmission radiative transfer code (MODTRAN) \citep{Berk1987}. At each time-step, a range of potential temperatures is specified (T\textsubscript{spec}) based on T\textsubscript{hem, b} calculated from the measured irradiance with

@@

After the LUT is defined, at-sensor spectral radiances for each path length/zenith angle are modeled at an emissivity of 0.95 over a waveband of 0 - 2300 \si{cm^{-1}} for each T\textsubscript{spec}. Profiles of T\textsubscript{air} and humidity are retrieved from 30-minute averages of conditions observed at the Sperrstrasse site. Aerosol, trace gas absorber, and above-sensor T\textsubscript{air} and humidity conditions are defined by the mid-latitude summer standard atmosphere when daytime T\textsubscript{air, max} \textgreater 10 \si{\degreeCelsius} (the mid-latitude winter profile is substituted on days where T\textsubscript{air, max} \textless 10 \si{\degreeCelsius}) \citep{Kantor1962}.

@@

MODTRAN has been shown to effectively model near-ground radiative transfer at urban-scale path lengths in 2-dimensions \citep{Hoch2005, Hoch2007}. However, the method described in this paper accounts for complex 3-dimensional surface geometry, which can exert significant influence on atmospheric transmittance. In addition, the method includes significant post-processing to weight and integrate point-to-point spectral directional radiances to derive 3-dimensional, hemispherical irradiances. Thus, prior to deriving a climatology of urban T\textsubscript{hem, r}, the method was evaluated using profiles of upwelling longwave irradiances measured over a simple planar surface.

@@

For a continuous 14-day period, profiles of up/downwelling short/longwave radiation, T\textsubscript{air}, and humidity measured from 2 \si{m}, 10 \si{m}, and 30 \si{m} were obtained from an instrumented tower in Payerne, Switzerland. The tower, installed over a cultivated field as a part of the Baseline Surface Radiation Network (BSRN), is located approximately 100 \si{\kilo\meter} southwest of the BUBBLE Sperrstrasse tower and is subject to similar summertime conditions as the study site. The study period was chosen to include a comprehensive range of T\textsubscript{surf}, T\textsubscript{air}, humidities, and cloud coverages to represent typical summertime conditions over which atmospheric corrections show the greatest variation. To evaluate the method, we used a modified version of the workflow described in Figure \ref{flow}. First, azimuthally averaged path lengths over a planar surface were calculated in SUM at 5\si{\degree} increments of zenith angle over the sensor FOV for the 10 \si{\meter} and 30 \si{\meter} sensors. For each time step, T\textsubscript{hem, b}, calculated from the lowest $L_z$ measurement, was used to model irradiances at 10 \si{m} and 30 \si{m} at 30-minute intervals using concurrent profiles of T\textsubscript{air} and humidity. Daytime T\textsubscript{air} observed at the highest measurement level was anomalously high compared to typical summertime lapse rates above planar vegetated terrain \citep{Oke1987}. Thus, the T\textsubscript{air} profile was modified to be more representative of the neutral or weakly unstable daytime conditions and weakly stable nighttime conditions. It is likely that these modifications better represent the T\textsubscript{air} profile in the layer between 10 and 30 \si{\meter} than a simple interpolation between the 10 \si{\meter} T\textsubscript{air} and 30 \si{\meter} T\textsubscript{air} measurements. Contrary to the findings in \citet{Kotani2009a}, an isothermal atmospheric profile was not sufficient to accurately model upwelling fluxes over planar terrain. Although thermal stratification is relatively small by day in an urban canyon \citep{Nakamura1988} - where strong microscale contrasts in T\textsubscript{surf} foster strong canyon mixing and neutral stability - the large daytime T\textsubscript{surf} - T\textsubscript{air} differential and the path-length/transmittance gradient can create large differences in upwelling longwave forced by inter-canyon thermal contrasts - a phenomenon termed radiative divergence. By underestimating near-surface air temperatures and overestimating roughness-layer T\textsubscript{air}, positive divergences by day are underestimated by an isothermal profile. As such, we suggest using a full canyon T\textsubscript{air} and humidity profile to most accurately model near ground fluxes.

@@

\begin{table}[H]
	\centering
	\caption{Statistical performance of the Payerne evaluation. RMSE\textit{\textsubscript{s}} and RMSE\textit{\textsubscript{u}} represent the systemic and unsystematic RMSE respectively. n = 378}
	\label{evalstats}
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}} cccr}
		\toprule 
		Statistic & 10 \si{\meter} flux & 30 \si{\meter} flux & Divergence & Citation \\  \midrule
		Slope & 1.002 & 1.011 & 0.792 &  \\ 
		Intercept, (\si{\watt\per\meter\squared}) & 0.422 & $-$3.560 & $-$0.583 &   \\ 
		\textit{R\textsuperscript{2}} & 0.995 & 0.996 & 0.863 & \\ 
		MAE,  (\si{\watt\per\meter\squared}) & 1.781 & 1.325 & 1.191 & \citep{Willmott1985a} \\ 
		RMSE,  (\si{\watt\per\meter\squared}) & 2.204 & 1.690 & 1.423 & \citep{Willmott1985a} \\ 
		RMSE\textit{\textsubscript{s}},  (\si{\watt\per\meter\squared}) & 1.444 & 0.851 & 1.028 & \citep{Willmott1985a} \\ 
		RMSE\textit{\textsubscript{u}},  (\si{\watt\per\meter\squared}) & 1.666 & 1.460 & 0.985 & \citep{Willmott1985a} \\ 
		\textit{d}, agreement index & 0.999 & 0.999 & 0.959 & \citep{Willmott2012} \\
		\bottomrule
	\end{tabular*} 
\end{table}

@@

Over both summer and winter seasons, correction magnitudes are strongly correlated with $\Delta$T\textsubscript{hem, r - air}. Figure \ref{season_fit} shows the effect of seasonality and cloud cover on the relationship between correction magnitudes and $\Delta$T\textsubscript{hem, r - air}. The relationship is strongest and most evident in summer when variations in cloud cover can lead to large day-to-day contrasts in solar input and $\Delta$T\textsubscript{surf - air}, which translates into a wide range of correction magnitudes.

Figure \ref{nofit} illustrates the relationship between correction magnitude and meteorological variables commonly measured as a part of climatological assessments of urban environments. A strong positive relationship is observed between correction magnitudes and incoming solar radiation. T\textsubscript{hem, r} and T\textsubscript{air} display more complex relationships with correction magnitude, with a large cluster of observed correction magnitudes situated at a local minimum between $10$ and $20$ \si{\degreeCelsius}, weakly negative correlation at temperatures lower than $10$ \si{\degreeCelsius}, and weakly positive correlation at temperatures greater than $20$ \si{\degreeCelsius}. Atmospheric water vapor content did not appear to exert significant control over correction magnitudes.

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,
	height=7in,
	keepaspectratio]{bx_ac1}
	\caption{Atmospheric correction magnitudes calculated as the difference between T\textsubscript{hem, r} and T\textsubscript{hem, b} for the duration of the study period. Grey shading indicates nighttime. The red line indicates mean correction magnitude at each time step.}
	\label{bx_ac}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,
	height=7in,
	keepaspectratio]{nofit}
	\caption{Correction magnitude versus meteorological variables for the daytime hours of the study period.}
	\label{nofit}
\end{figure}

@@

@@

Mean normalized T\textsubscript{hem, r}, T\textsubscript{plan}, and $\Delta$T\textsubscript{plan - hem, r} are shown in figure \ref{tc_mean} along with clear sky and overcast sky case days. While mean T\textsubscript{hem, r} and T\textsubscript{plan} display similar overestimations of T\textsubscript{comp}, under clear sky conditions, overestimation by T\textsubscript{plan} is much larger than that by T\textsubscript{hem, r}.

@@
